\sysfull

### 2018-08-03 paper/asplos19/intro.tex
change the paragraph about paper structure

\begin{figure} %{t!}{0.45\textwidth}
    \centering
    \includegraphics[width=\columnwidth]{figures/intro-figure-tiny.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{cmt} in the figure). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}

@@

% \textbf{Contributions.} To summarize, \sys's main contributions are:
% %
% \begin{itemize}
% \item The first {\em adaptive} task-based intermittent execution model that
% dynamically \emph{coalesces} tasks to reduce commit overhead and
% \emph{downscales} tasks to ensure forward progress.
% \item The first memory virtualization mechanism that preserves the atomicity of coalesced tasks under power failures.
% %\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
% \item A fully-realized prototype of \sys that runs on real energy-harvesting devices, to be released as open source after publication via~\cite{coala_website}.
% \item An evaluation directly comparing \sys to a state of the art task-based
% intermittent programming and execution model from prior work, showing that on a
% suite of benchmarks from the literature and several new workloads, \sys often
% has higher performance and is more flexible to diverse energy conditions.
% \end{itemize}
%
Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while
Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism (coalescing and downscaling). Memory virtualization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
context of related work and Section~\ref{sec:conclusions} concludes and discusses
future work.

>>>>

\begin{figure} %{t!}{0.45\textwidth}
    \centering
    \includegraphics[width=\columnwidth]{figures/intro-figure-vert.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{cmt} in the figure). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{figure}

@@

% \textbf{Contributions.} To summarize, \sys's main contributions are:
% %
% \begin{itemize}
% \item The first {\em adaptive} task-based intermittent execution model that
% dynamically \emph{coalesces} tasks to reduce commit overhead and
% \emph{downscales} tasks to ensure forward progress.
% \item The first memory virtualization mechanism that preserves the atomicity of coalesced tasks under power failures.
% %\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.
% \item A fully-realized prototype of \sys that runs on real energy-harvesting devices, to be released as open source after publication via~\cite{coala_website}.
% \item An evaluation directly comparing \sys to a state of the art task-based
% intermittent programming and execution model from prior work, showing that on a
% suite of benchmarks from the literature and several new workloads, \sys often
% has higher performance and is more flexible to diverse energy conditions.
% \end{itemize}
%
Section~\ref{sec:background} provides background on intermittent computing.
Section~\ref{sec:systemdescription} provides an overview of \sys, while
Section~\ref{sec:task_adaptation} describes \sys's task adaptation mechanism. Dynamic group privatization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are given in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
context of related work and Section~\ref{sec:conclusions} concludes and discusses
future work.
